---
title: "Assignment_2"
author: "Mr. GULAB PATEL"
date: "26/09/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Import packages to read excel file
```{r}
library(readxl)
```

#Prepare data
```{r}
ActuatorData1 <- read_excel("/cloud/project/ISI_BLR_Data_Processing_R/ISI_R_Assignment_2/Gulab Patel - Actuator_Data.xlsx")
head(ActuatorData1)
```

#Delete the "SL_No"
```{r}
ActuatorData = ActuatorData1[,c(-1)]
head(ActuatorData)
```

#Summary of data
```{r}
summary(ActuatorData)
```

# Import caret package
```{r}
library(caret)
```

# making the data format as data frame
```{r}
ActuatorData = as.data.frame(ActuatorData)
```


# Separate x's and y
```{r}
x = ActuatorData[,c("Bearing_to_bearing_Length","Driver_Shaft_length","Worm_length","Thickness","Height","Height","Load")]
y = ActuatorData$Torque_Variation
head(x)
```

#Converting y to a categorical variable
```{r}
y = as.factor(y)
```


# Data Visualization FeaturePlot
```{r}
featurePlot(x,y,plot = "density",
            scales= list(x = list(relation = "free"),
                         y = list(relation = "free")),
                         pch = "", adjust = 2.5,
                         layout = c(4,2),
                         auto.key = list(columns = 3))
```
#From the above boxplot figure, we can say that "Bearing_to_bearing_Length" has the most influence on torque variation



#When y is categorical can use BoxPlot
```{r}
featurePlot(x,y,plot = "box",
            scales= list(x = list(relation = "free"),
                         y = list(relation = "free")),
                         layou = c(4,2))
```
#From the above boxplot figure, we can say that "Bearing_to_bearing_Length" has the most influence on torque variation





# Question 2
#Import package to read excel file
```{r}
library(readxl)
```


```{r}
Resolution_Time_Data1 <- read_excel("/cloud/project/ISI_BLR_Data_Processing_R/ISI_R_Assignment_2/Gulab Patel - Resolution_Time_Data.xlsx")
head(Resolution_Time_Data1)
```

#Delete the first column
```{r}
ResolutionTimeData = Resolution_Time_Data1[,c(-1)]
head(ResolutionTimeData)
```
# a
# Summary
```{r}
summary(ResolutionTimeData)
```
#Our dataset contains missing values



# Replace missing values using "knnImpute" method

#To do the KNN imputation implementation, change data to dataframe
```{r}
ResolutionTimeData = as.data.frame(ResolutionTimeData)
```


#Import caret package
```{r}
library(caret)
```

```{r}
install.packages("RANN")
library(RANN)
```
#K-NN imputation with k = 4
```{r}
mypreprocess = preProcess(ResolutionTimeData, method = "knnImpute", k=4)
mypreprocess
```

```{r}
ResolutionTimeData = predict(mypreprocess, ResolutionTimeData)
head(ResolutionTimeData)
```

#(b)
##Data Vizualization
# Separate x's and y
```{r}
x = ResolutionTimeData[,1:3]
y = ResolutionTimeData$Resolution_Time
```

#Data visualization
```{r}
featurePlot(x,y, plot = "scatter")
```
#Above scatter plot shows that the explanatory variables and resolution time has the positive corelation. From the scatter plot, it seems that Volume is impacting resolution time most.





#(c)
#Feature Selection - Linear Regression
```{r}
mycontrol = rfeControl(functions = lmFuncs,
                       method = "repeatedcv",
                       repeats = 5,
                       verbose = T)
```


```{r}
myModellm = rfe(x, y, rfeControl = mycontrol)
myModellm
```

#Feature Selection - Random Forest
```{r}
mycontrol = rfeControl(functions = rfFuncs,
                       method = "repeatedcv",
                       repeats = 5,
                       verbose = T)
```


```{r}
myModelrf = rfe(x,y,rfeControl = mycontrol)
myModelrf
```
# Feature selection algorithm shows that all the explanatory variables are influencing resolution time.
```{r}
name <- function(variables) {
  
}
```

