---
title: "ISI_Data_Processing"
author: "Mr. GULAB PATEL"
date: "18/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##Module 6 Data Transformations
```{r}
library(readxl)
TAT <- read_excel("/cloud/project/ISI_BLR_Data_Processing_R/Dataset/TAT.xlsx")
head(TAT)
```


```{r}
summary(TAT)
```


```{r}
library(psych)
describe(TAT)
```
#Z transformation
```{r}
myzdata = scale(TAT)
describe(myzdata)
```

#Compute minimum of the fields
```{r}
mins = apply(TAT, 2, min)
mins
```

#Compute maximum of the fields
```{r}
maxs = apply(TAT, 2, max)
maxs
```

# Min-max transformation
```{r}
tr_data = scale(TAT,center = mins,scale = maxs-mins)
describe(tr_data)
```

#Module 7 Imputation method
#Advanced techniques for replacing missing values:
#1. k nearest neighbor method
#2. Bagging method


#1. KNN method
```{r}
SP1 <- read_excel("/cloud/project/ISI_BLR_Data_Processing_R/Dataset/Preprocessing_Data_I.xlsx")
SP2 <- read.csv("/cloud/project/ISI_BLR_Data_Processing_R/Dataset/Preprocessing_Data_II.csv")
```

```{r}
#head(SP1)
#head(SP2)
```

#Aggregate the files
```{r}
#mydat <- rbind(SP1,SP2)
#head(mydat)
```
#feature names does not matches so let's check which feature differ from corresponding feature in the second file.
```{r}
for(i in 1:ncol(SP1))
{
 print(identical(names(SP1[i]), names(SP2[i])))
}
```
#First feaure doesn't match, now make them same
```{r}
colnames(SP1)[colnames(SP1)=="SL No"]<-names(SP2[1])
names(SP1[1])
```

```{r}
mydat <- rbind(SP1,SP2)
head(mydat)
```

#Remove SL No filed
```{r}
mydat=mydat[,c(-1)]
head(mydat)
```

#Summary of mydat
```{r}
summary(mydat)
```

#To do the KNN implementation, change mydat to dataframe
```{r}
mydat = as.data.frame(mydat)
```

```{r}
install.packages("caret")
```

#Import caret package
```{r}
library(caret)
```

```{r}
install.packages("RANN")
library(RANN)
```

#K-NN imputation with k = 4
```{r}
mypreprocess = preProcess(mydat, method = "knnImpute", k=4)
mypreprocess
```

```{r}
knn_data = predict(mypreprocess, mydat)
knn_data
```



#Bagging Imputation
```{r}
myprocess_bagg = preProcess(mydat, method="bagImpute")
bag_data = predict(myprocess_bagg, mydat)
bag_data
```

#Import package to read excel file
```{r}
library(readxl)
```

#Module 8 Data Visualization
```{r}
ChemYield <- read_excel("/cloud/project/ISI_BLR_Data_Processing_R/Dataset/Chemical_Yield.xlsx")
ChemYield
```
#Cleanup data by deleting "SL No"
```{r}
ChemYield = ChemYield[,c(-1)]
ChemYield
```

# Data Summary
```{r}
summary(ChemYield)
```

# Import caret package
```{r}
library(caret)
```

# making the data format as data frame
```{r}
ChemYield = as.data.frame(ChemYield)
ChemYield
```

# Imputing missing values using Bagging imputation
```{r}
preprocess = preProcess(ChemYield, method = "bagImpute")
ChemYield = predict(preprocess, ChemYield)               
ChemYield
```

# Separate x's and y
```{r}
x = ChemYield[,1:3]
y = ChemYield$Yield
```

#Data visualization
```{r}
featurePlot(x,y, plot = "scatter")
```


```{r}
DefectPron <- read_excel("/cloud/project/ISI_BLR_Data_Processing_R/Dataset/Defect_Proneness.xlsx")
DefectPron
```
```{r}
summary(DefectPron)
```

# seperating x's and y
```{r}
x = DefectPron[,1:8]
y = DefectPron$Defect_Prone
```


#Converting y to a categorical variable
```{r}
y = as.factor(y)
```

# Data Visualization FeaturePlot
```{r}
featurePlot(x,y,plot = "density",
            scales= list(x = list(relation = "free"),
                         y = list(relation = "free")),
                         pch = "", adjust = 2.5,
                         layout = c(4,2),
                         auto.key = list(columns = 3))
```

#When y is categorical can use BoxPlot
```{r}
featurePlot(x,y,plot = "box",
            scales= list(x = list(relation = "free"),
                         y = list(relation = "free")),
                         layout = c(4,2))
```



# Module 9 Feature Selection
## Recursive Feature Elimination Method
### Steps:
#1. Fit a model with all features
#2. Validate model
#3. Calculate accuracy or score
#4. Remove the least contributing feature
#5. Fit the model with remaining features and go back to step 2
#Generally accuracy is estimated using cross validation
```{r}
SP1 <- read_excel("/cloud/project/ISI_BLR_Data_Processing_R/Dataset/Preprocessing_Data_I.xlsx")
SP2 <- read.csv("/cloud/project/ISI_BLR_Data_Processing_R/Dataset/Preprocessing_Data_II.csv")
```

#First feaure doesn't match, now make them same
```{r}
colnames(SP1)[colnames(SP1)=="SL No"]<-names(SP2[1])
names(SP1[1])
```
# Prepare the dataset
```{r}
mydata = rbind(SP1, SP2)
head(mydata)
```

#Cleanup dataset by removing "SL_No field
```{r}
mydata1 = mydata[,c(-1)]
head(mydata1)
```

#Seperate x's and y
```{r}
x = mydata1[,1:8]
y = mydata1$Sprint_Prod
```

#Import caret library
```{r}
library(caret)
```

#replacing the missing values in x using Bagging imputation
```{r}
mypreprocess = preProcess(x,method="bagImpute")
x = predict(mypreprocess, x)
```

#Feature Selection - Linear Regression
```{r}
mycontrol = rfeControl(functions = lmFuncs,
                       method = "repeatedcv",
                       repeats = 5,
                       verbose = T)
```


```{r}
myModellm = rfe(x, y, rfeControl = mycontrol)
myModellm
```

#Feature Selection - Random Forest
```{r}
mycontrol = rfeControl(functions = rfFuncs,
                       method = "repeatedcv",
                       repeats = 5,
                       verbose = T)
```


```{r}
myModelrf = rfe(x,y,rfeControl = mycontrol)
myModelrf
```


#example when responce variable is categorical
## Import biospy data from MASS package(we can download the data from MASS package too)
```{r}
library(MASS)
Biopsy = biopsy #read_csv("/cloud/project/ISI_BLR_Data_Processing_R/Dataset/biopsy.csv")
head(Biopsy)
```
#Clean the data by removing "ID" Field
```{r}
Biopsy1 = Biopsy[,c(-1)]
head(Biopsy1)
```

#Summary data
```{r}
summary(Biopsy1)
```
# deleting records with missing values use the following code
```{r}
Biopsy1 = na.omit(Biopsy1)
Biopsy1
```

# Seperate x and y
```{r}
x = Biopsy1[,1:9]
y = Biopsy1$class
```

# Feature selection using linear discriminant function
```{r}
mycontrollda = rfeControl(functions = ldaFuncs,
                       method = "repeatedcv",
                       repeats = 5,
                       verbose = T)
```

#For LDA we need to install package "e1071"
```{r}
install.packages("e1071")
library(e1071)
```

```{r}
myModellda = rfe(x,y, rfeControl = mycontrollda)
myModellda
```

# Feature selection using random forest function
```{r}
mycontrol = rfeControl(functions = rfFuncs,
                       method = "repeatedcv",
                       repeats = 5,
                       verbose = T)
```


```{r}
myModel = rfe(x,y, rfeControl = mycontrol)
myModel
```

